Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2014-09-20 ms.tex
Fixing some equation numbers

First, by demanding continuity of the entropy derivative at the stagnation radius, the temperature at the stagnation radius is given by (equation~[\ref{eq:Tanalytic}])
\begin{align}
T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v_{w}^{2}}{2} \approx 6
\times 10^6\,v_{500}^2 \, \mu  \,\,{\rm K} 
\end{align}
%{\bf BDM: i picked $\mu = 0.62$ and stick to it.}

Next, by demanding hydrostatic equilibrium at the stagnation point, an expression for the stagnation radius can be derived (equation~[\ref{eq:rstag}]),
\begin{align}
  \x=\frac{1}{\zeta^2 n}\left[
    \frac{\Mstar}{\Mbh}\left(A-\frac{n}{2}\right)+(B-\frac{n}{2})\right],
  \label{eq:stag_analytic}
\end{align}
where $\zeta \equiv v_{w,0}/\sigma$, $r_{\rm soi}
=GM_{\bullet}/\sigma^{2}$ is the radius of the SMBH sphere of
influence (soi), and A and B are constants that depend on the Nuker
parameter $\Gamma$ and the adiabatic index of the gas.

>>>>

First, by demanding continuity of the entropy derivative at the stagnation radius, the temperature at the stagnation radius is given by.
\begin{align}
T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v_{w}^{2}}{2} \approx 6
\times 10^6\,v_{500}^2 \, \mu  \,\,{\rm K} 
\label{eq:Tanalytic}
\end{align}
%{\bf BDM: i picked $\mu = 0.62$ and stick to it.}

Next, by demanding hydrostatic equilibrium at the stagnation point, an expression for the stagnation radius can be derived,
\begin{align}
  \x=\frac{1}{\zeta^2 n}\left[
    \frac{\Mstar}{\Mbh}\left(A-\frac{n}{2}\right)+(B-\frac{n}{2})\right],
  \label{eq:stag_analytic}
\end{align}
where $\zeta \equiv v_{w,0}/\sigma$, $r_{\rm soi}
=GM_{\bullet}/\sigma^{2}$ is the radius of the SMBH sphere of
influence (soi), and A and B are constants that depend on the Nuker
parameter $\Gamma$ and the adiabatic index of the gas.
